(Re)building cooperation: Effects of a cognitive intervention on cooperative behavior in games

### 2024-01-29 article.Rmd
changed transparency statement

## Disclosures {.unnumbered}

Conflicts of interest: The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
Funding: Author 1 was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1. Author 3 acknowledges support by the UCLH NIHR BRC. He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
Ethics: This research received approval from a local ethics board (ID:21029/001).
Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
Reproducibility: The results are fully reproducible, and all data and code for the analyses (including the manuscript in R Markdown format) are available on: https://github.com/ismailg/coax_psych_science. The design and analysis plans were not preregistered.

@@

```{r modAllReturns, include=FALSE, cache=TRUE}

@@

#prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
#cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
```

@@

```{r modInvs, include=FALSE, cache=TRUE}
mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| playerId), avg_ret_df, method="KR")
summary(mod_invs)
anova(mod_invs)

@@

```{r, include=FALSE, cache=TRUE}
# ALL ROUNDS BEFORE DEFECTION TRIAL
pre_int_data <- avg_ret_df %>% filter(roundType=="trust",!is.na(gameNum.f),(roundNum < 12 & gameNum.f =="pre")| (roundNum < 13 & gameNum.f =="post"))

@@

@@

# # Define the vertical line data
# vline_data <- data.frame(
#   xintercept = c(12, 13),
#   linetype = c("Pre-manipulation", "Post-manipulation"),  # Names corresponding to the existing scale
#   roundGroup = c("Rounds 11-15", "Rounds 11-15")
# )

@@

# afex_plot(mod_emo_x, x = "gameNum.f", trace = "condition.f", dodge = 0.8, error = "within",
#             data_geom = geom_violin, 
#             data_arg = list(width = 0.5))
#

# library(GGally)
# ggpairs(datCoax %>% dplyr::select(emo_scaled_x,emo_scaled_y,inv_scaled))

@@

```{r, include=FALSE}
# Install the 'psych' package
if (!requireNamespace("psych", quietly = TRUE)) {
  install.packages("psych")
}

# Load the 'psych' package
library(psych)

questionnaires <- avg_ret_df %>% group_by(playerId) %>% dplyr::select(PBOR_score,DERS_score,RFQ_c) %>% unique() %>% ungroup()
# Perform EFA
efa_result <- fa(questionnaires %>% dplyr::select(PBOR_score,DERS_score,RFQ_c), nfactors = 2, fm = "minres", rotate = "varimax")
# Print the EFA result
print(efa_result)

```{r, include=FALSE}
turing <- read_csv("data/turing.csv")
colnames(turing) <- c("responses", "category")

@@

@@

for(i in n_state_min:n_state_max) {

  # rModels <- rep(list(list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment))),each=i)

  ###########################################################
  mus <- (1:i)*(1/(i+1))
  sigmas <- rep(1/(i+1), i)
  rModels <- list()
  for(s in 1:i) {
    rModels[[s]] <- list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment, pstart=c(mus[s],sigmas[s])))
  }
  #########################################################

>>>>

## Research Transparency Statement {.unnumbered}

### General Disclosures {.unnumbered}

Conflicts of interest: The author(s) declared that there were no conflicts of interest with respect to the authorship or the publication of this article.
Funding: Author 1 was supported by the UK Engineering and Physical Sciences Research Council under grant EP/S515255/1. Author 3 acknowledges support by the UCLH NIHR BRC. He has received fees and options for consultancies for Aya Technologies and Alto Neuroscience.
Ethics: This research received approval from a local ethics board (ID:21029/001).
Artificial intelligence: No artificial intelligence assisted technologies were used in this research or the creation of this article.
Reproducibility: [The authors are applying for a Computational Reproducibility Badge which will be awarded pending checks by the STAR Team.]

### Study Disclosures {.unnumbered}

Preregistration: The hypotheses and methods were not preregistered.The analysis plan was not preregistered. Materials: All study materials are publicly available (https://github.com/ismailg/coax_psych_science). Data: All primary data are publicly available (https://github.com/ismailg/coax_psych_science). Analysis scripts: All analysis scripts are publicly available (https://github.com/ismailg/coax_psych_science).

@@

<!-- Linear mixed effects model for all returns  -->
```{r modAllReturns, include=FALSE, cache=TRUE}

@@

```{r modemmeans, include=F, cache=TRUE }
prepost_bycond <- pairs(emmeans::emmeans(mod_returns_pct, c("gameNum.f"), by = "condition.f", pbkrtest.limit = 9400))
cond_effect <- pairs(emmeans::emmeans(mod_returns_pct, c("condition.f"), by="gameNum.f"))
```

<!-- Secondary analyses for effect size and correlation between repeated measures.  -->
```{r, include=F}

@@

<!-- Linear mixed effects model for Investments -->
```{r modInvs, include=FALSE, cache=TRUE}
mod_invs <- mixed( investment ~ gameNum.f*condition.f  + (1 + gameNum.f| playerId), avg_ret_df, method="KR")
summary(mod_invs)
anova(mod_invs)

@@

<!-- Linear fixed effects model for returns: ALL ROUNDS BEFORE DEFECTION TRIAL -->
```{r, include=FALSE, cache=TRUE}

pre_int_data <- avg_ret_df %>% filter(roundType=="trust",!is.na(gameNum.f),(roundNum < 12 & gameNum.f =="pre")| (roundNum < 13 & gameNum.f =="post"))

@@

<!-- Linear fixed effects model for returns: ALL ROUNDS AFTER DEFECTION TRIAL -->
```{r, include=FALSE, cache=TRUE}

@@

@@

@@

<!-- Analyse participants response to Turing test -->
```{r, include=FALSE}
turing <- read_csv("data/turing.csv")
colnames(turing) <- c("responses", "category")

@@

<!-- Here we extend the depmixS4 package functionality for analyzing data using hidden Markov models (HMMs). It involves defining new response classes and their associated methods. -->

@@

for(i in n_state_min:n_state_max) {
  ###########################################################
  mus <- (1:i)*(1/(i+1))
  sigmas <- rep(1/(i+1), i)
  rModels <- list()
  for(s in 1:i) {
    rModels[[s]] <- list(vtdgaus(y=avg_ret_df$ret_pct_0,yield=3*avg_ret_df$investment, pstart=c(mus[s],sigmas[s])))
  }
  #########################################################
